\section{Administration}
\label{sec:administration}
To ensure that the server is operated properly, careful thought must be put towards the administration of a server. In particular, it is important a user is appointed to maintain financial responsibility to ensure payments are received and bills are paid on time. Another important aspect is technical responsibility. Intuitively, providing each user with root-level access is unwanted as this can easily lead to system instability. For this reason, a user will also need to bear technical responsibility. Lastly, one user must provide oversight for the entire project, reporting to the rest of the users key information, and overseeing that democratic decisions properly realized. It is solely these three people who should have access to the administrative accounts to manage the server.

\subsection{Oversight}
The Wyvern director is responsible for ensuring that the desires of the Wyvern users are respected and followed. The director directly reports to all Wyvern users about important issues, and attempts to resolve issues in de decision making process, should they arise.

\subsection{Financial Responsibility}
The Wyvern chief of finance manages the financial aspect of the server. It is this user who pays bills, and this user who receives payments from each user. The chief of finance is responsible that bills are paid on time, and that the correct amount of money is received from each user.

\subsection{Technical Responsibility}
The Wyvern chief of technology manages the technical aspect of the server. Whenever applications are requested to be installed, this user will attempt to do so. In addition, this user is responsible for the security aspect of the server, ensuring each user may connect in a secure manner, and that the Wyvern server is up to date with the latest security patches.
