\section{The Wyvern Community}
\label{sec:wyvern-community}
\begin{enumerate}
    \item Wyvern was established on the 21st of March 2017 in Delft.

    \item The objective of Wyvern is to satisfy the needs of its members in the context of gaming and computer server hosting.

    \item Wyvern is comprised of Wyvern members which are collectively known as the Wyvern community.

    \item Membership is granted with approval of the Wyvern community through majority vote.
    
    \begin{item}
        Membership is terminated:
        \begin{enumerate}
            \item through indication to the Board of Directors;
            \item through suspension, to be decided by the Board of Directors or unanimous vote;
            \item through expulsion, to be decided by unanimous vote.
        \end{enumerate}
    \end{item}

    \item Wyvern's primary asset is a shared networked computer (the~'server').

    \item Wyvern has a Board of Directors comprised of Wyvern members. The Board of Directors acts in behalf of and represents the Wyvern community.

    \item The Board of Directors is elected by majority vote for the duration of six months (one 'term'). At the end of a term, the Board of Directors is re-elected.

    \item The Board of Directors consists of at least three members: the \emph{Chairman}, the \emph{Chief of Finance}, and the \emph{Chief of Technology}.

    \begin{item}
        The responsibilities and duties of the Chairman are:
        \begin{enumerate}
            \item to represent the interests and desires of all Wyvern members;
            \item to oversee the Board of Directors, ensuring the Board of Directors is in compliance with the policies laid out in this document and the wishes of the Wyvern community;
            \item to facilitate Wyvern meetings, ensuring the democratic process is properly adhered to;
            \item to plan and reserve a space for Wyvern meetings;
            \item to create and publish the meeting agendas;
            \item to promote good communication and resolve conflicts within the Wyvern community.
        \end{enumerate}
    \end{item}

    \begin{item}
        The responsibilities and duties of the Chief of Finance are:
        \begin{enumerate}
            \item to act as treasurer, managing Wyvern funds;
            \item to ensure the external financial obligations of the Wyvern community are met;
            \item to ensure the internal financial obligations of Wyvern members are met;
            \item to record and update financial transactions and information related to the Wyvern server;
            \item to act as secretary during Wyvern community and board meetings, documenting all Wyvern discussions and votes, unless decided otherwise;
            \item to oversee other financial aspects of the Wyvern community.
        \end{enumerate}
    \end{item}

    \begin{item}
        The responsibilities and duties of the Chief of Technology are:
        \begin{enumerate}
            \item to ensure the proper functioning of the Wyvern server;
            \item to implement technical changes on the Wyvern server in accordance with the desires of the Wyvern community;
            \item to track changes of Wyvern server and report on these during community meetings;
            \item to manage security-related aspects of the Wyvern server, thus ensuring a secure working environment for Wyvern members.
        \end{enumerate}
    \end{item}

    \begin{item}
        The Board of Directors may independently suspend Wyvern members.
        \begin{enumerate}
            \item The duration of the suspension is at most until the next Wyvern meeting;
            \item The Wyvern community must be notified of the suspension immediately;
            \item Suspension may be overruled in community meetings by majority vote.
       \end{enumerate}
    \end{item}

    \item Whenever there are ambiguities or contradictions in the articles of association, the guidelines, or the rules, the Board of Directors decides upon the matter. Appeal is possible at community meetings.

    \item At the discretion of the Wyvern community meeting, committees may be erected.

    \item Committees are comprised of Wyvern members are under the authority and oversight of the Board of Directors.

    \item Unless decided otherwise, committee members are appointed, suspended, and discharged through a community meeting.

    \item Committees may convene and act independently of the Wyvern community.

    \item Committees may manage and use assets, which may include monetary assets. All committee assets are under the authority of the Board of Directors.

    \begin{item}
            Commissions may raise, manage, and expend funds independently and autonomously subject to a budget.
            \begin{enumerate}
                \item Committee budgets require ratification from the Board of Directors team before they are put into effect.
                \item Committee budgets must be settled before committees members are discharged. The settlement requires ratification from the Board of Directors team.
                \item Post-settlement, any remaining credit is entrusted to the Board of Directors as Wyvern funds.
            \end{enumerate}
    \end{item}

    \item Committees may be dissolved during community meetings through a vote.

    \item Wyvern may only be dissolved by unanimous vote. After dissolution, the remaining Wyvern assets are divided equally among the community.

\end{enumerate}
