\section{Financial}
\label{sec:financial}

\begin{enumerate}
    \item Wyvern obtains funds through member contribution and any other lawful means.

    \item The Chief of Finance manages the funds. They may be stored in cash or electronically on a bank account managed by the Chief of Finance.

    \item All Wyvern members have financial responsibility. Financial responsibility includes the obligation to pay contribution or incurred damages (or fraction thereof) within the timespan and with the conditions to be decided upon by the administration team.

    \begin{item}
        All members must pay contribution.
        \begin{enumerate}
            \item The contribution fee is decided by the administration team. The minimum contribution is $C_m = \frac{S-F}{M}$ euros and the maximum contribution is $C_m = \frac{S}{M} + 5$ euros, where $C_m$ is the individual member contribution, $S$ is the costs for the upkeep of the server for the next term, $F$ is the amount of Wyvern funds, and $M$ is the amount of Wyvern members in the next term.
            \item The contribution fee for the next term is calculated at the end of a term and is fixed for the duration of the next term.
        \end{enumerate}
    \end{item}

    \item With exception of article \ref{sec:financial}.\ref{itm:funds}, the Chief of Finance may only expend Wyvern funds with approval from the Wyvern community through a vote.

    \begin{item}
         In case of unexpected costs resulting from the operation of the Wyvern server, services hosted by the Wyvern community, or by services hosted by members of the Wyvern community, the Director must host an exceptional community meeting to discuss this topic.
        
        \begin{enumerate}
            \item During such an exceptional meeting, the origin of the unexpected financial damage must be determined and the extent of the damage must be quantified.

            \begin{item}
                The meeting must decide by majority vote one of the following:

                \begin{enumerate}
                    \item \label{itm:damage-negligence} The financial damage has as basis the negligence of a single Wyvern member or a group thereof.
                    \item \label{itm:damage-normal} The financial damage has as basis the normal operation of Wyvern services.
                \end{enumerate}
            \end{item}

            \item In case that article \ref{sec:financial}.\ref{itm:damage-negligence} holds true, the financial responsibility is placed upon the responsible Wyvern member or group thereof.

            \item In case that article \ref{sec:financial}.\ref{itm:damage-normal} holds true, the shared financial responsibility is placed equally upon all Wyvern members.
        \end{enumerate}

    \end{item}
\end{enumerate}
