\section{The LAN Committee}

\begin{enumerate}
	\item At the discretion of the Wyvern community meeting, a LAN committee may be erected.
	
    \item The objective of the LAN committee is to organize and host LAN gaming events.
    
	\item The LAN committee consists of at least three members: a \textit{Chairman}, a \textit{Administration Team Deputy}, and a \textit{Commissioner of Activities}.

    \begin{item}
        The responsibilities and duties of the Chairman of the LAN committee are:
        \begin{enumerate}
            \item to plan and reserve a space for LAN committee meetings;
            \item to facilitate LAN committee meetings;
            \item to seek for and appoint a suitable commissioner of activities for the LAN committee;
            \item to guide and oversee all financial aspects of the LAN committee;
            \item to lead the LAN registration process;
            \item to inform the Wyvern community on the status of the LAN.
        \end{enumerate}
    \end{item}
    
    \begin{item}
        The responsibilities and duties of the Commissioner of Activities of the LAN committee are:
        \begin{enumerate}
            \item to set a suitable date and location for the LAN event;
            \item to purchase and prepare sufficient provisions for the LAN event;
            \item to act as secretary during LAN committee meetings, documenting all committee discussions and votes, unless decided otherwise.
        \end{enumerate}
    \end{item}
    
    \begin{item}
        The responsibilities of the Administration Team Deputy of the LAN committee are:
        \begin{enumerate}
            \item to facilitate communication between the LAN committee and the administration team;
            \item to report the progress of the LAN committee to the administration team;
            \item to discuss the budget of the LAN committee with the administration team and to ratify it when consensus has been reached;
            \item to otherwise aid in the organization of the LAN event.
        \end{enumerate}
    \end{item}
    
    \begin{item}
        The Chairman of the LAN committee may, after each LAN event, discharge and appoint the Commissioner of Activities.
        \begin{enumerate}
            \item The Chairman may become Acting-Commissioner of Activities. To do so, the Chairman must first appoint an Interim-Chairman to facilitate the role of Chairman for that LAN event.
            \item Upon completion of the LAN event, the Interim-Chairman may be discharged by the Acting-Commissioner of Activities.
        \end{enumerate}
    \end{item}

    \item The LAN committee may convene and discuss the organization of LAN events independently of the Wyvern community.
    
    \item The LAN committee may charge attendees a share of the expenses upon completion of the LAN event.
    
    \item The LAN committee may charge non-Wyvern attendees an additional premium for attending the LAN event. The LAN committee must properly inform attendees of this premium.
    
    \item The LAN committee may purchase goods and services for the benefit of the LAN event.
    
    \item After each LAN attendee has paid their fees, the LAN committee must meet to settle any outstanding debts incurred throughout the organization of the LAN event. In the event that a positive balance remains, the administration team will govern over any remaining funds.
    
    \item The Commissioner of Activities may exclude certain non-Wyvern members for attending the LAN event before the LAN event has commenced.
    
    \begin{item} If a LAN attendee causes significant disarray or damage of property, the LAN committee may, in consensus, impose certain sanctions upon that member:
        \begin{enumerate}
            \item expulsion from the grounds; or
            \item charging an additional fee for incurred costs.
        \end{enumerate}
    \end{item}
    
    \item If a LAN attendee causes significant disarray or damage of property, the LAN committee may, in consensus, request the Wyvern community to exclude said attendee from future LAN events. In such a case, a vote must be held to decide upon the matter.

\end{enumerate}
\newpage