\section{Administration}
\label{sec:administration}
To ensure that the server is operated properly, careful thought must be put towards the administration. In particular, it is important one user is appointed to maintain financial responsibility in order to ensure each member's contribution is received and bills are paid on time. Another important aspect is technical responsibility. Intuitively, providing each user with root-level access is undesirable as this can easily lead to catastrophic disasters. For this reason, one user will need to bear technical responsibility. Lastly, one user must provide oversight for the entire community. This user reports to the rest of the members key information, and oversees that democratic decisions properly realized. Solely these three people should have access to the administrative accounts to manage the server.

\subsection{Director}
The Wyvern Director is responsible for ensuring that the desires of the Wyvern community are respected. The Director directly reports to all Wyvern users about important issues and attempts to resolve these in community meetings. The Director is responsible for organizing and hosting these meetings. During a Wyvern meeting, the Director oversees the democratic voting process.

\subsection{Chief of Finance}
The Wyvern Chief of Finance manages all financial aspects of the server. This user is responsible with paying bills and receiving payments from all other users. The Chief of Finance must ensure that bills are paid on time and that the correct amount of money is received from each user. In addition, the Chief of Finance has the additional role of secretary and therefore must take notes during community meetings.

\subsection{Chief of Technology}
The Wyvern Chief of Technology manages the technical aspect of the server. This user is tasked with managing and satisfying the technical needs of Wyvern community members. In addition, this user is responsible for the security aspects of the server, ensuring each user may connect in a secure manner and that the Wyvern server is up to date with the latest security patches. Additionally, the Chief of Technology must keep track of all technical changes to the server and report these during community meetings.

